Exploring probability distributions for bivariate temporal granularities

### 2019-09-23 main.Rmd
changing season to make analysis more interesting

MI_winner <- cricket_winner %>% 
             filter(batting_team ==  "Mumbai Indians" | bowling_team == "Mumbai Indians",
                    season %in% c(2010:2015)) %>% 
             mutate(win = if_else(winner == "Mumbai Indians", 1, 0))

CSK_winner <- cricket_winner %>% 
             filter(batting_team ==  "Chennai Super Kings"| bowling_team == "Chennai Super Kings",
                    season %in% c(2010:2015)) %>% 
             mutate(win = if_else(winner == "Chennai Super Kings", 1, 0))

@@

```{r}
cricket_winner %>% as_tibble() %>% 
             filter(batting_team ==  "Mumbai Indians" | bowling_team == "Mumbai Indians",
                    winner!= "Mumbai Indians",
                    win_by_runs!=0) %>% select(win_by_runs) %>% summary()

cricket_winner %>% as_tibble() %>% 
             filter(batting_team ==  "Chennai Super Kings",
                    winner!= "Chennai Super Kings",
                    win_by_runs!=0,
                    inning ==2) %>% select(win_by_runs) %>% summary()
```

@@

 cricket_tsibble_all %>% 
  filter(season %in% c(2010:2015), batting_team=="Mumbai Indians") %>% 
           granplot("inning", "over",
                               hierarchy_model,
                               response = "run_rate",
                               plot_type = "lv",
                               quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9))  + ggtitle("")

 cricket_tsibble_all %>% 
  filter(season %in% c(2010:2015), batting_team=="Chennai Super Kings",
         inning %in% c(1,2)) %>% 
           granplot("inning", "over",
                               hierarchy_model,
                               response = "run_rate",
                               plot_type = "lv",
                               quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9)) + ggtitle("")

>>>>

MI_winner <- cricket_winner %>% 
             filter(batting_team ==  "Mumbai Indians" | bowling_team == "Mumbai Indians",
                    season %in% c(2013, 2015)) %>% 
             mutate(win = if_else(winner == "Mumbai Indians", 1, 0))

CSK_winner <- cricket_winner %>% 
             filter(batting_team ==  "Chennai Super Kings"| bowling_team == "Chennai Super Kings",
                    season %in% c(2013, 2015)) %>% 
             mutate(win = if_else(winner == "Chennai Super Kings", 1, 0))

@@

```{r}
cricket_winner %>% as_tibble() %>% 
             filter(batting_team ==  "Mumbai Indians" | bowling_team == "Mumbai Indians",
                    winner!= "Mumbai Indians",
                    win_by_runs!=0,
                    season %in% c(2013, 2015)) %>% select(win_by_runs) %>% summary()

cricket_winner %>% as_tibble() %>% 
             filter(batting_team ==  "Chennai Super Kings",
                    winner!= "Chennai Super Kings",
                    win_by_runs!=0,
                    inning ==2, 
                    season %in% c(2013, 2015)) %>% select(win_by_runs) %>% summary()
```

@@

 cricket_tsibble_all %>% 
  filter(season %in% c(2013, 2015), batting_team=="Mumbai Indians") %>% 
           granplot("inning", "over",
                               hierarchy_model,
                               response = "run_rate",
                               plot_type = "lv",
                               quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9))  + ggtitle("")

 cricket_tsibble_all %>% 
  filter(season %in% c(2013, 2015), batting_team=="Chennai Super Kings") %>% 
           granplot("inning", "over",
                               hierarchy_model,
                               response = "run_rate",
                               plot_type = "lv",
                               quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9)) + ggtitle("")
